Growing libraries of concepts with wake-sleep program induction

### 2018-07-20 talk.tex
Turtle part of the slides

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
\usepackage{listings}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

@@

\begin{frame}{DSL: Library of concepts}
\includegraphics[width = 11cm]{3DSL.png}
\end{frame}

@@

\begin{frame}{Turtle graphics}
  Created+Investigated by Mathias Sabl\'e Meyer

@@

  \begin{itemize}
  \item pen up/pen down
  \item move pen (forward+rotate)
  \item get/set pen state
  \item `for' loops
  \end{itemize}

  \centering
  \includegraphics[width = 8cm]{exampleGraphicsPrograms.png}

\end{frame}
\begin{frame}{Turtle graphics}
  Created+Investigated by Mathias Sabl\'e Meyer

  \includegraphics[width = 10cm]{turtleFigure.png}

>>>>

\documentclass{beamer}
\usetheme{metropolis}
\usepackage{listings}
\usepackage{amsfonts}
\usepackage{dsfont}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage{verbatim}
%\usepackage{tipa}
\usepackage{tikz}
\usetikzlibrary{fit}
\usepackage{color}
\usepackage{booktabs}
\usepackage{tipa}
\usepackage{amssymb}
\usepackage{verbatim}
\usepackage[absolute,overlay]{textpos}
\usepackage{pifont}% http://ctan.org/pkg/pifont
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\usetikzlibrary{bayesnet}
\usetikzlibrary{decorations.markings}
\usetikzlibrary{decorations.pathmorphing}
\tikzset{squiggle/.style={decorate, decoration={snake,amplitude=.4mm}}}
\usepackage{xcolor}
\definecolor{pop1}{HTML}{1F78b4}
\definecolor{pop2}{HTML}{164C13}
\definecolor{pop3}{HTML}{d95F02}
\definecolor{orange}{HTML}{d95F02}
\definecolor{teal}{HTML}{1b9e77}
\newcommand{\pop}[1]{\textcolor{pop1}{#1}}
\newcommand{\popp}[1]{\textcolor{pop2}{#1}}
\newcommand{\tree}[1]{\textcolor{pop3}{#1}}
\newcommand{\orange}[1]{\textcolor{orange}{#1}}
\newcommand{\teal}[1]{\textcolor{teal}{#1}}

@@

\usepackage[most]{tcolorbox}
\definecolor{block-gray}{gray}{0.10}
\newtcolorbox{mycode}{colback=block-gray,grow to right by=0mm,grow to left
by=0mm, boxrule=0pt,boxsep=0pt,breakable,fontupper=\color{white}}

@@

\begin{frame}{DSL: Library of concepts}
\Wider[5.4em]{
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \footnotesize\begin{tabular}{cc}
    \toprule
Tasks and     \pop{Programs} & DSL\\
    \midrule
      \begin{tabular}{cc}
        \begin{tabular}{c}
          \code{[7\, 2\, 3]}$\to$\code{[7\, 3]}         \\
          \code{[1\, 2\, 3\, 4]}$\to$\code{[3\, 4]} \\
          \code{[4\, 3\, 2\, 1]}$\to$\code{[4\, 3]} \\
          \pop{\code{$f(\ell) = $}\code{($f_1$ $\ell$ ($\lambda$ (x)}}\\
          \hspace{1.15cm}\pop{\code{(> x 2)))}}       \\
          \\
          \\
          \code{[2\, 7\, 8\, 1]}$\to $\code{8}               \\
          \hspace{0.15cm}\code{[3\, 19\, 14]}$\to $\code{19}                \\
          \pop{\code{$f(\ell) = $}\code{($f_2$ $\ell$)}}
        \end{tabular}
        &
        \hspace{-0.3cm}\begin{tabular}{c}
          \code{[7\, 3]}$\to $\code{False}                              \\
          \hspace{0.3cm}\code{[3]}$\to $\code{False}                    \\
          \hspace{-0.3cm}\code{[9\, 0\, 0]}$\to $\code{True\phantom{e}} \\
          \hspace{0.3cm}\code{[0]}$\to $\code{True\phantom{e}}                        \\
          \hspace{-0.3cm}\code{[0\, 7\, 3]}$\to $\code{True\phantom{e}}                \\
          \pop{\code{$f(\ell) = $}\code{($f_3$ $\ell$ 0)}}
        \end{tabular}
      \end{tabular}
    &
    \begin{tabular}{l}
      \popp{$f_0(\ell,$\code{r}$) \,=\, $\code{(foldr r $\ell$ cons)}}\\
      \hspace{\helpSize}($f_0$: \emph{Append lists }\code{r}\emph{ and  $\ell$})\\
      \popp{$f_1(\ell,$\code{p}$) \,=\, $\code{(foldr $\ell$ nil ($\lambda$ (x a)}}\\
      \hspace{0.5cm}\popp{\code{(if (p x) (cons x a) a)))}}\\
      \hspace{\helpSize}($f_1$: \emph{Higher-order filter function})\\
      %(lambda (fold $0 0 (lambda (lambda (if (gt? $0 $1) $0 $1)))))
      \popp{$f_2(\ell) \,=\, $\code{(foldr $\ell$ 0 ($\lambda$ (x a)}}\\
      \popp{\phantom{$f_2(\ell) \,=\, $}\code{(if (> a x) a x)))}}\\
      \hspace{\helpSize}($f_2$: \emph{Maximum element in list $\ell$})\\
      \popp{$f_3(\ell,$\code{k}$) \,=\, $\code{(foldr $\ell$ (is-nil $\ell$)}}\\
      \phantom{$f_1(\ell,$}
      \popp{\code{($\lambda$ (x a) (if a a (= k x))))}}\\
      \hspace{\helpSize}($f_2$: \emph{Whether $\ell$ contains }\code{k})\\
    \end{tabular}
  \\\bottomrule
  \end{tabular}
}
\end{frame}

@@

\begin{frame}{Turtle graphics}

  \begin{block}{DSL}
    \texttt{FW x | RT x | UP | DOWN | SET state}
  \end{block}

  \begin{block}{Tasks}
    \texttt{unit -> image}
  \end{block}

@@

  \only<1>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \vspace*{5\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/line.eps}
    \end{columns}
  }
  \only<2>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle.eps}
    \end{columns}
  }
  \only<3>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \texttt{RT} $\frac\pi2$\\
          \texttt{FW 1}\\
          \vspace*{1\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/angle2.eps}
    \end{columns}
  }
  \only<4>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(4)}\\
          \texttt{> FW 1}\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{3\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/square.eps}
    \end{columns}
  }
  \only<5>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> FW 1} \\
          \texttt{> SET origin} \\
          \texttt{> RT} $\frac{2\pi}{8}$\\
          \vspace*{2\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/star.eps}
    \end{columns}
  }
  \only<6>{
    \begin{columns}[T]
      \column{0.5 \textwidth}
        \begin{mycode}
          \texttt{for i in range(8)}\\
          \texttt{> PU} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> PD} \\
          \texttt{> FW} $\frac{\text{\texttt{i}}}{2}$\\
          \texttt{> RT} $\frac\pi2$\\
          \vspace*{0\baselineskip}
        \end{mycode}
      \column{0.5 \textwidth}
        \includegraphics[width = 4cm]{figures/teachLogo/spiral.eps}
    \end{columns}
  }
\end{frame}

\begin{frame}{Turtle graphics}
  \centering
  \includegraphics[width=11cm]{figures/tasksMinusBehaviour.png}
\end{frame}
